Data Pre-Processing

### 2021-04-27 AST-Framing-Ontario/Data Pre-Processesing.rmd
April 26th Changes

Load the following packages:
```{r}
library(tm)
library(readr)
library(tools)
library(dplyr)
library(tidytext)
library(topicmodels)
library(ggplot2)
library(wordcloud)
```

@@

Municipalities or regions have general webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis. Only webpages specifically dicussing active travel, AST, or STP were included. Webpages were also sourced from associated public health units becasues their direct relation to governing bodies at the municipal or regional level.

@@

```{r}
pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Municipalities or Regions"

@@

NAwords <- c("school", "transportation", "can", "use", "active", "et al", "travel", "j", "behav" , "nutr", "phys", "int", "n", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "s", "the")
corpus <- tm_map(corpus, removeWords, NAwords)
corpus <- tm_map(corpus, removeNumbers)

@@

# Example
content(corpus[[1]])
```

@@

The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code. The code below utilizes LDA, an algorithm that when provided a number of desrete topics, 'k', will calculate the likelyhood of any given term being generated in a given topic. This algorithm runs under the 'bag of words' assumptions with means grammatic structre (adjective, noun, verb) is not considered. Words are rather considered 
```{r}
# k represents the number of topics to be generated by the algorithm 
k <- 5
lda <- LDA(DTM, k, control = list(seed = 1234))

@@

```{r}
v <- sort(rowSums(matrix1), decreasing= TRUE)
d <- data.frame(word = names(v), freq=v)
set.seed(4321)
wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
```

@@

This code is a is a version of the code in the 'AST-Framing-Ontario.Rmd'. It is condensed into a single block to allow the iterative conversion each subfolder. Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
```{r}
# Iterating through each subfolders 
m <- 1
for (subFolder in subFolders){

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned  corpuses 
```{r}
# n - number of corpora
n <- 3
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

@@

>>>>

Load the following packages:
```{r}
library(tm)
library(readr)
library(tools)
library(dplyr)
library(tidytext)
library(topicmodels)
library(ggplot2)
library(wordcloud)
library(word2vec)
```

@@

Municipalities or regions have webpages about transportation plans, programs, and services provided, some of which are not relevent to our analysis. Only webpages specifically dicussing active travel, AST, or STP were included. Webpages were also sourced from associated public health units becasues their direct relation to governing bodies at the municipal or regional level.

@@

Location:

"E:/Github/AST-Framing-Analysis-Ontario/Texts/Academic Papers"
"E:/Github/AST-Framing-Analysis-Ontario/Texts/Consortia"
"E:/Github/AST-Framing-Analysis-Ontario/Texts/Municipalities or Regions"
"E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"

```{r}
pdfLocation <- "E:/Github/AST-Framing-Analysis-Ontario/Texts/School Boards"

@@

NAwords <- c("contact", "cancellations", "catholic", "waterloo", "board", "east", "transportation", "students", "student", "website", "tri", "can", "district", "will", "please", "may", "school", "https")
corpus <- tm_map(corpus, removeWords, NAwords)
corpus <- tm_map(corpus, removeNumbers)

@@

# Example
content(corpus[[5]])
```

@@

The goal of topic modelling is to identify the re-occurring themes in our corpus quantitatively with code. The code below utilizes LDA, an algorithm that when provided a number of desrete topics, 'k', will calculate the likelyhood of any given term being generated in a given topic. This algorithm runs under the 'bag of words' assumptions with means grammatic structre (adjective, noun, verb) is not considered. Words are rather considered 
```{r}
# k represents the number of topics to be generated by the algorithm 
k <- 4
lda <- LDA(DTM, k, control = list(seed = 1234))

@@

```{r}
v <- sort(rowSums(matrix1), decreasing= TRUE)
d <- data.frame(word = names(v), freq=v)
set.seed(4321)
wordcloud(d$word, d$freq, min.freq = 10, max.words = 50, random.order = FALSE, rot.per = 0.5, random.color = TRUE)
```
# Word to Vector Test
https://m-clark.github.io/text-analysis-with-R/word-embeddings.html 
```{r}
library(text2vec)

# Need to create new data frame with the cleaned corpus 
cleanTextDF <- data.frame(text = sapply(corpus, as.character), stringsAsFactors = FALSE)

it_train = itoken(cleanTextDF$text, progressbar = FALSE)
vocab = create_vocabulary(it_train)

# Cuts out terms that have a minimum count of 5 
vocab <- prune_vocabulary(vocab, term_count_min = 5)
vocab

vectorizer <- vocab_vectorizer(vocab)
tcm <- create_tcm(it_train, vectorizer, skip_grams_window = 10)

glove = GlobalVectors$new(rank = 50, x_max = 10)
main = glove$fit_transform(tcm, n_iter = 10, convergence_tol = 0.001)
context = glove$components

word_vectors = main + t(context)

safe = word_vectors["mental", , drop = FALSE]

cos_sim = sim2(x = word_vectors, y = safe, method = "cosine")

head(sort(cos_sim[,1], decreasing = TRUE), 10)

@@

Corpora will be cleaned for white spaces, punctuations, English stopwords, and converted to lowercases. Any additional stopwords will need to be removed manually as the user sees fit. 
```{r}
# Iterating through each subfolders 
m <- 1
for (subFolder in subFolders){

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned corpora.
```{r}
# n - number of corpora
n <- 3
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", toString(i), sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

@@

# Vector Sort

```{r}
sort(NAwords)
```
